Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-04-14 Text/Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
One more line

In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous domains, in particular between gamma and \(\mathcal{G}^0\) distributed data, each with a known number of looks. 
To understand the core ideas behind our approach, we explore the use of properties such as entropy and coefficient of variation.

>>>>

In this context, we present a set of three novel test statistics that aim to distinguish between homogeneous and non-homogeneous return, in particular between gamma and \(\mathcal{G}^0\) distributed data, assuming the number of looks is known. 
We use properties such as entropy and coefficient of variation.
